---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

http://voteview.org/page2a.htm

## Common Space DW-NOMINATE Scores 1st to 113th Congresses
(http://voteview.org/dwnomin_joint_house_and_senate.htm)

```{r common, fig.width = 5, fig.height = 5, fig.cap = "100th Congress, 1987-89", echo = FALSE}
vizip::polarization2D(all = TRUE)
```

## Weekly Constant Space DW-NOMINATE Scores
(http://voteview.org/Weekly_Constant_Space_DW-NOMINATE_Scores.htm)

```{r weekly, fig.width = 5, fig.height = 5, fig.cap = "100th Congress, 1987-89", echo = FALSE}
vizip::polarization2D(data.version = "common.weekly", all = TRUE)
```

##  DW-NOMINATE Scores 1st to 113th Congresses
(http://voteview.org/dwnomin.htm)

```{r dw, fig.width = 5, fig.height = 5, fig.cap = "100th Congress, 1987-89", echo = FALSE}
vizip::polarization2D(data.version = "dw", all = TRUE)
```
